Viscous Transport in Eroding Porous Media

### 2019-06-14 docs/transport/erosion_transport.tex
do the result in transport paper

In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
from the starting cross section x = -1 to 
the end cross section x = 1 and 
use the local tortuosity to analysis the effect
of the geometrical structure on fluid velocity field when the porosity is 62.9 \%.
In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281
\times 10^{-4}$ at equal spreading tracers on the starting cross section.
The velocity is continuous along the starting cross section and
acting as several Poiseuille flows. This velocity graph is different
from the one in~\cite{matyka2008tortuosity} since we choose our cross
section to be the beginning of the flow before the fluid touches any
body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
$\tau(y)=\lambda(y)/d$
of the tracers at $y$ on the starting cross section x = -1 
where $d = 2$.
This graph is not continuous
and the jumps in $\tau$ mean that the initial neighboring tracers have been
seperated by the bodies. 
}

@@

{\color{red}
In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of 
$\tau$ at two neighboring tracers 
and draw the trajectories of neighboring tracers in 
Fig.~\ref{fig:Eroding20tort_traj}
if the difference of $\tau$ at the neighboring tracers is large. 
From Fig.~\ref{fig:Eroding20tort_traj},
 we are able to tell the neighboring trajectories will be very 
different if they are separated by bodies. In Fig.~\ref{fig:Eroding20tort_traj}
we collect the 10 largest difference of $\tau$ at the neighboring tracers and 
draw the pair of trajectories in the same color. For each pair of trajectories, 
they are splitted by the body at the left side of the body, then
one of them goes up and the other one goes down along the body 
until they rejoin with each other at the right side of body.  
Furthermore, the pair trajectories could be splitted by more than one body, 
for example in Fig.~\ref{fig:Eroding20tort_traj} the toppest red pair trajectories 
are splitted by two close bodies. (?)
}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc20_268}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local20_268}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/diff_tort20_268}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/uminDumax20_268}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies.
(a) The 
x-component velocity u(-1, y) with respect to its maximum velocity $u_{max}=6.2281
\times 10^{-4}$ at equal spreading tracers on the cross section x = -1. 
(b) The local tortuosity $\tau(y)$ on the cross section x = -1. 
(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
\end{figure}

@@

To measure the local behavior of fluid quantitatively, 
we use the velocities and local tortuosities at the starting cross section 
to analysis the interaction of fluid and bodies until the end cross section 
in Fig.~\ref{fig:Eroding100tort}.
In Fig.~\ref{fig:Eroding100tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=3.9021
\times 10^{-4}$ at equal spreading tracers on the strating cross section.
As in the case of 20 nearly touching bodies, the velocity is continuous along
the starting cross section and acting as a Poiseuille flow in the channel between
bodies. But the velocity of the fluid with 100 bodies on the starting cross section 
changes more rapidly than the velocity of the fluid with 20 bodies 
and the local maximum velocity of the fluid with 100 bodies 
on the starting cross section is higher than the maximum velocity 
of the fluid with 20 bodies. The reason of the rapid change and 
high velocity on the starting cross section of 100-body case is because there are 
more bodies near the starting cross section in
100-body case than in the 20-body case. So the inlet flow in 100-body case
will be separated into more branches than the flow in 20-body case. 
Furthermore, under the fixed pressure drop condition the speed of flow in a channel is faster 
when the channel is smaller.

In Fig.~\ref{fig:Eroding100tort_traj}

>>>>

In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
from the starting cross section x = -1 to 
the end cross section x = 1 and 
use the local tortuosity to analysis the effect
of the geometrical structure on fluid velocity field when the porosity is 62.9 \%.
In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=2.9828
\times 10^{-3}$ at equal spreading tracers on the starting cross section.
The velocity is continuous along the starting cross section and
acting as several Poiseuille flows. This velocity graph is different
from the one in~\cite{matyka2008tortuosity} since we choose our cross
section to be the beginning of the flow before the fluid touches any
body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
$\tau(y)=\lambda(y)/d$
of the tracers at $y$ on the starting cross section x = -1 
where $d = 2$.
This graph is not continuous 
and the jumps in $\tau$ mean that the initial neighboring tracers have been
seperated by the bodies. 
The maximum of $\tau$ is 1.2713 and the minimum is 1.0001.
}

@@

{\color{red}
In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of 
$\tau$ at two neighboring tracers 
and draw the trajectories of neighboring tracers in 
Fig.~\ref{fig:Eroding20tort_traj}
if the difference of $\tau$ at the neighboring tracers is large. 
From Fig.~\ref{fig:Eroding20tort_traj},
 we are able to tell the neighboring trajectories will be very 
different if they are separated by bodies. In Fig.~\ref{fig:Eroding20tort_traj}
we collect the 10 largest difference of $\tau$ at the neighboring tracers and 
draw the pair of trajectories in the same color. For each pair of trajectories, 
they are splitted by the body at the left side of the body, then
one of them goes up and the other one goes down along the body 
until they rejoin with each other at the right side of body.  
Furthermore, the pair trajectories could be splitted by more than one body, 
for example in Fig.~\ref{fig:Eroding20tort_traj} the toppest red pair trajectories 
are splitted by two close bodies.
}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc20_268}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local20_268}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/diff_tort20_268}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/uminDumax20_268}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies.
(a) The 
x-component velocity u(-1, y) with respect to its maximum velocity $u_{max}=2.9828
\times 10^{-3}$ at equal spreading tracers on the cross section x = -1. 
(b) The local tortuosity $\tau(y)$ on the cross section x = -1. 
(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
\end{figure}

@@

To measure the local behavior of fluid quantitatively, 
we use the velocities and local tortuosities at the starting cross section 
to analysis the interaction of fluid and bodies until the end cross section 
in Fig.~\ref{fig:Eroding100tort}.
In Fig.~\ref{fig:Eroding100tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=3.9021
\times 10^{-4}$ at equal spreading tracers on the strating cross section.
As in the case of 20 nearly touching bodies, the velocity is continuous along
the starting cross section and acting as a Poiseuille flow in the channel between
bodies. When the fluid is close to bodies
the speed of fluid will be slow down because of the no-slip condition on the bodies
and this causes the separated branches of the inlet flow.
The maximum velocity of the fluid with 100 bodies on the starting cross 
section is slower than the maximum velocity of the fluid with 20 bodies
but the velocity in the case of 100 bodies 
changes more rapidly than the velocity of the fluid with 20 bodies.
The reason of the rapid change on the starting cross section of 
100-body case is because there are 
more bodies near the starting cross section in
100-body case than in the 20-body case. 
so the inlet flow in 100-body case
will be separated into more branches than the flow in 20-body case.

In Fig.~\ref{fig:Eroding100tort}(b) we record the 
local tortuosity $\tau(y)$ for $y$ on the starting cross section x = -1.
It is a discontinous function and the maximum of $\tau$ in the case of 100 bodies is

has more jumps than the one in the case of 20 bodies. 
The jump in this graph means the neighboring trajectories are splitted by bodies
so it is reasonable to have more jumps in the case of 100-body than the case of 20-body
since there are more bodies in the former case. In Fig.~\ref{fig:Eroding100tort}(c) 
we use the data we got from local tortuosity $\tau(y)$
to find the difference of $\tau$ at the neighboring tracers and
draw 50 pairs of neighboring trajectories which have the largest difference of $\tau$
in Fig.~\ref{fig:Eroding100tort_traj}. 
The maximum of $\tau$ is 1.2547 and the minimum is 1.0003.
